A finite-state morphological transducer for Kyrgyz

### 2012-03-14 paper/paper.tex
typo

\abstract{This paper describes the development of a free/open-source finite-state morphological transducer for Kyrgyz. The transducer 
has been developed for morphological generation for use within a prototype Turkish$\rightarrow$Kyrgyz machine translation system, but has also be extensively tested for analysis. The finite-state toolkit used for the work was the Helsinki Finite-State 
Toolkit (HFST). The paper describes some issues in Kyrgyz morphology, the development of the tool, some linguistic issues encountered and how they were dealt with, and 
which issues are left to resolve. An evaluation is presented which shows that the transducer has medium-level coverage, between 82\% and 87\% on two freely available corpora of Kyrgyz, and high precision and recall over a manually verified test set. \\
\Keywords{kyrgyz, morphology, transducer}}

>>>>

\abstract{This paper describes the development of a free/open-source finite-state morphological transducer for Kyrgyz. The transducer 
has been developed for morphological generation for use within a prototype Turkish$\rightarrow$Kyrgyz machine translation system, but has also been extensively tested for analysis. The finite-state toolkit used for the work was the Helsinki Finite-State 
Toolkit (HFST). The paper describes some issues in Kyrgyz morphology, the development of the tool, some linguistic issues encountered and how they were dealt with, and 
which issues are left to resolve. An evaluation is presented which shows that the transducer has medium-level coverage, between 82\% and 87\% on two freely available corpora of Kyrgyz, and high precision and recall over a manually verified test set. \\
\Keywords{kyrgyz, morphology, transducer}}
